\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Pankaj Kumar} \\ 
    \small \href{tel:+918101865933}{ \raisebox{-0.1\height}\faPhone\ \underline{+91-8101865933} ~} \href{mailto:pankaj.ky3007@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{pankaj.ky3007@gmail.com}} ~
    \href{https://www.linkedin.com/in/pankaj-kumar-5bbb44268/}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{Linkedin}}  ~
    \href{https://github.com/PankajKumar1947}{\raisebox{-0.2\height}\faGithub\ \underline{Github}} ~
    \href{https://leetcode.com/u/pankajkry/}{\raisebox{-0.2\height}\faCode\ \underline{LeetCode}} ~
    \vspace{-4pt}
\end{center}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Asansol Engineering College, Asansol}{2022 -- 2026}
      {B.Tech- Computer Science and Engineering - \textbf{CGPA} - \textbf{8.6}}{ Asansol, West Bengal}
  \resumeSubHeadingListEnd
 
  \resumeSubHeadingListStart
    \resumeSubheading
      {B L Indo Anglian Public School}{2019 -- 2021}
      {Science  }{Aurangabad, Bihar}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
    {PLANTROOT NEXTGEN TECHNOLOGIES PRIVATE LIMITED}{Aug, 2025 -- Current}
    {\underline{Software Developer Intern}}{Remote}
    \resumeItemListStart
      \resumeItem{Contributed to a large-scale \textbf{HRMS platform} managing \textbf{employees, projects, vendors, and clients}, supporting end-to-end organizational workflows.}
      \resumeItem{Developed workforce and operations modules including \textbf{time-off management}, \textbf{timesheets}, \textbf{weekly status reports (WSR)}, and \textbf{asset tracking} with role-based access control.}
      \resumeItem{Engineered scalable and maintainable frontend features using \textbf{Next.js} and \textbf{Tailwind CSS}, with reusable UI components built using \textbf{shadcn/ui} and \textbf{tablecn}.}
      \resumeItem{Handled large datasets and API integrations using \textbf{TanStack Table} and \textbf{TanStack Query}, implementing optimized \textbf{queries, mutations, pagination, filtering}, and caching strategies.}
    \resumeItemListEnd



  \resumeSubheading
    {GrowthPurple Technologies}{March, 2025 -- Aug, 2025}
    {\underline{Software Engineering Intern}}{Remote}
    \resumeItemListStart
      \resumeItem{Built a \textbf{GenAI-powered full-stack platform Pluton} which generate deployable \textbf{React}, \textbf{Next.js}, and \textbf{Vue} code from prompts, rendered live with \textbf{WebContainers} for an \textbf{IDE-like browser experience}.}
      \resumeItem{Designed a \textbf{personal cloud storage system} to manage and reuse image assets across projects, \textbf{reducing duplication by 60\%} and improving delivery speed.}
      \resumeItem{Integrated \textbf{PostgreSQL}, \textbf{cron jobs}, and \textbf{Dodo Payments} to support \textbf{scalable data workflows}, \textbf{automated tasks}, and \textbf{seamless transactions}.}
      \resumeItem{Enabled users to \textbf{create, preview, deploy, and sell AI-generated web apps} through a \textbf{built-in marketplace} with full end-to-end flow.}
    \resumeItemListEnd  

\resumeSubHeadingListEnd


%------RELEVANT COURSEWORK-------
% \section{COURSEWORK / SKILLS}
%     \begin{multicols}{4}
%         \begin{itemize}[itemsep=-2pt, parsep=5pt]
%             \item Data Structures \& Algorithms
%             \item Operating Systems
%             \item Network Security
%             \item Database Management System (DBMS)
%             \item Artificial Intelligence
%             \item OOPS Concept
%             \item Web Development
%             \item Android Development
%         \end{itemize}
%     \end{multicols}
%     \vspace*{2.0\multicolsep}

%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-3pt}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\href{https://mycodingnotes.vercel.app/}{\textbf{\large{\underline{MyCodingNotes}}} \href{https://mycodingnotes.vercel.app/}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{React, Typescript, Postgresql, Hono, Tailwind CSS, Prisma}}}{April, 2024 - Present}
          \resumeItemListStart
          \vspace{5pt}
            \resumeItem{\normalsize{Developed \textbf{MyCodingNotes}, a web platform designed for students and educators to securely create, store, and share notes, with \textbf{SEO optimization} to improve discoverability and engagement.}}
            \resumeItem{\normalsize{Enhanced user experience with secure \textbf{JWT authentication}, efficient media management, and tracking of user behavior through \textbf{Firebase Analytics} for actionable insights.}}
            \resumeItem{\normalsize{Implemented a \textbf{markdown-based text editor}, enabling seamless content creation, and integrated \textbf{Firebase Storage} for fast, reliable image hosting.}}
          \resumeItemListEnd
      \resumeSubHeadingListEnd
      
  \resumeSubHeadingListStart
  \vspace{-20pt}
   \resumeProjectHeading
      {\href{https://github.com/PankajKumar1947/snap-study}{\textbf{\large{\underline{SnapStudy}}} \href{https://github.com/PankajKumar1947/snap-study}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{React, Tailwind CSS, HTML, JavaScript, API}}}{Jan, 2024 - April, 2024}
      \resumeItemListStart
      \vspace{5pt}
        \resumeItem{\normalsize{Developed \textbf{SnapStudy}, a platform to enhance academic resources for engineering students preparing for upcoming semester exams.}}
        \resumeItem{\normalsize{Frontend: \textbf{React JS} with \textbf{React-router-dom}, \textbf{Tailwind CSS} for styling, Integrated \textbf{JSON Data} for dynamic content rendering.}}
        \resumeItem{\normalsize{Data: Utilized \textbf{GitHub} hosting for \textbf{JSON data}, enabling easy updates and maintenance.}}
        \resumeItem{\normalsize{Implemented \textbf{Google Drive} for storing PDFs, generating links, and hosting them on GitHub Pages.}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


      
      
%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Languages}{: C++, C, JavaScript, Typescript, SQL}}
    \resumeSubItem{\textbf{Technologies/Frameworks}{: React, NextJs, Postgres, MongoDb, Express, Nodejs}}
    \resumeSubItem{\textbf{Developer Tools}{: VS Code, Postman, Git, Github, npm, Docker}}
  \resumeSubHeadingListEnd
  
%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS}
  \resumeSubHeadingListStart
    \resumeItem{\normalsize{Solved 700+ Problems on Leetcode and maintained the maximum streak of 365 days.}}
    \resumeItem{\normalsize{Conceptualized, designed, and launched  \textbf{SnapStudy}\href{https://snapstudy-makaut.vercel.app/}{\raisebox{-0.1\height}\faExternalLink }, a comprehensive study material platform for MAKAUT students, attracting an average of 10 students daily, enhancing academic resources.}}
  \resumeSubHeadingListEnd
  
\end{document}
